Extended Abstract

### 2021-05-24 paper/paper.tex
Use theorem envs, refer to theorems in discussion

\renewcommand*{\sectionautorefname}{\S\!\!\,}
\renewcommand*{\subsectionautorefname}{\S\!\!\,}

@@

\paragraph{Inference Soundness}

Given $\tEq{\func{infer}~p}{\gamma , \Gamma , cs}$, every substitution \(\sigma\) that makes the constraints $cs$ hold makes $\tProc{(\subst{\sigma}{\Gamma})}{p}$ hold.

\paragraph{Inference Completeness}

Given $\tEq{\func{infer}~p}{\gamma , \Gamma , cs}$, for every context \(\Delta\) that makes $p$ typable, there exists a substitution \(\sigma\) that solves the constraints $cs$ such that $\Delta$ is a specialisation of $(\subst{\sigma}{\Gamma})$ --- a specialisation $\Delta ~ \func{\subseteq} ~ (\subst{\sigma}{\Gamma})$ is defined as $\exists \sigma_f . ~ \tEq{\Delta}{(\subst{\sigma_f}{(\subst{\sigma}{\Gamma})})}$.

@@

\paragraph{Resolution Soundness}

Given $\tEq{\func{solve}~cs_1}{(\sigma, cs_2)}$, every substitution $\sigma_f$ that satisfies the simplified constraints ($\interpr{\subst{\sigma_f}{cs_2}}$) satisfies the original constraints after substitutions are applied ($\interpr{\subst{\sigma_f}{(\subst{\sigma}{cs_1})}}$).

\paragraph{Resolution Completeness}

Given $\tEq{\func{solve}~cs_1}{(\sigma, cs_2)}$, any substitution \(\sigma_f\) that makes the original constraints \(cs_1\) hold ($\interpr{\subst{\sigma_f}{cs_1}}$) can be decomposed into $\sigma$ followed by a certain \(\sigma_g\) ($\sigma_f ~ \type{\doteq} ~ \sigma_g \cdot \sigma$) that makes the returned constraints \(cs_2\) hold ($\interpr{\subst{\sigma_g}{cs_2}}$).

\paragraph{Resolution Progress}

Given $\func{solve}~cs_1 \equiv (\sigma, cs_2)$, to keep us from returning the original constraints as output (which is both sound and complete), we postulate that none of the constraints $c \in cs_2$ has a most general solution, where a most general solution for a constraint $c$ is defined as $\exists \sigma. ~ \interpr{\subst{\sigma}{c}} \times (\forall \sigma_f . ~ \interpr{\subst{\sigma_f}{c}} \times (\exists \sigma_g. ~ \sigma_f ~ \type{\doteq} ~ \sigma_g \cdot \sigma))$.

@@

We have outlined a procedure for decidable type checking and inference of a \picalc{} with linear and shared types.
Constraint collection and constraint resolution are kept separate, and their metatheory allows for deferred constraints.
We have proven in Agda that constraint collection and the resolution of equality constraints is sound, the remaining proofs are still in progress.

>>>>

\theoremstyle{definition}\newtheorem{mytheorem}{Theorem}[section]
\renewcommand*{\sectionautorefname}{\S\!\!\,}
\renewcommand*{\subsectionautorefname}{\S\!\!\,}

@@

\begin{mytheorem}[Inference Soundness]\label{inference-soundness}
Given $\func{infer}~p$ returns $\gamma , \Gamma , cs$, every substitution \(\sigma\) that makes the constraints $cs$ hold makes $\tProc{(\subst{\sigma}{\Gamma})}{p}$ hold.
\end{mytheorem}

\begin{mytheorem}[Inference Completeness]\label{inference-completeness}
Given $\func{infer}~p$ returns $\gamma , \Gamma , cs$, for every context \(\Delta\) that makes $p$ typable, there exists a substitution \(\sigma\) that solves the constraints $cs$ such that $\Delta$ is a specialisation of $(\subst{\sigma}{\Gamma})$ --- a specialisation $\Delta ~ \func{\subseteq} ~ (\subst{\sigma}{\Gamma})$ is defined as $\exists \sigma_f . ~ \tEq{\Delta}{(\subst{\sigma_f}{(\subst{\sigma}{\Gamma})})}$.
\end{mytheorem}

@@

\begin{mytheorem}[Resolution Soundness]\label{resolution-soundness}
Given $\func{solve}~cs_1$ returns $(\sigma, cs_2)$, every substitution $\sigma_f$ that satisfies the simplified constraints ($\interpr{\subst{\sigma_f}{cs_2}}$) satisfies the original constraints after substitutions are applied ($\interpr{\subst{\sigma_f}{(\subst{\sigma}{cs_1})}}$).
\end{mytheorem}

\begin{mytheorem}[Resolution Completeness]\label{resolution-completeness}
Given $\func{solve}~cs_1$ returns $(\sigma, cs_2)$, any substitution \(\sigma_f\) that makes the original constraints \(cs_1\) hold ($\interpr{\subst{\sigma_f}{cs_1}}$) can be decomposed into $\sigma$ followed by a certain \(\sigma_g\) ($\sigma_f ~ \type{\doteq} ~ \sigma_g \cdot \sigma$) that makes the returned constraints \(cs_2\) hold ($\interpr{\subst{\sigma_g}{cs_2}}$).
\end{mytheorem}

\begin{mytheorem}[Resolution Progress]\label{resolution-progress}
Given $\func{solve}~cs_1$ returns $(\sigma, cs_2)$, to keep us from returning the original constraints as output (which is both sound and complete), we postulate that none of the constraints $c \in cs_2$ has a most general solution, where a most general solution for a constraint $c$ is defined as $\exists \sigma. ~ \interpr{\subst{\sigma}{c}} \times (\forall \sigma_f . ~ \interpr{\subst{\sigma_f}{c}} \times (\exists \sigma_g. ~ \sigma_f ~ \type{\doteq} ~ \sigma_g \cdot \sigma))$.
\end{mytheorem}

@@

We have outlined a procedure for decidable type checking and inference of a \picalc{} with linear and shared types.
Constraint collection and constraint resolution are kept separate, and their metatheory allows for deferred constraints.
We have proved in Agda the soundness of constraint collection \autoref{inference-soundness} and of equality constraint resolution \autoref{resolution-soundness}, the remaining proofs are still in progress.
